COG-ED Manuscript

### 2021-12-13 06_Paper/COG-ED/Manuscript.Rmd
NHB guidelines: shortened title to less than 100 characters

---
title             : "When easy is not preferred: The Cognitive and Emotion Regulation Effort Discounting paradigm (CERED) for estimating subjective values of cognitive tasks"
shorttitle        : "The CERED paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    affiliation   : "1,*"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    affiliation   : "1,*"
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
  * Shared first authorship
abstract: |
  Every day, individuals have to weigh the value of the reward when reaching a goal against the required effort.
  However, effort is not inherently aversive to all individuals, which has often been neglected by previous approaches to quantify the subjective value of effort.
  One of them is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013), which can quantify the subjective values of the difficult levels of the n-back task against the easiest level.
  We aim to replicate the analysis of Westbrook et al. (2013) with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm (CERED).
  The CERED paradigm will likely enable a more insightful investigation of interindividual differences in effort discounting, as well as the investigation of effort discounting for task types for which this is currently not possible due to their high degree of subjectivity.

>>>>

---
title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
shorttitle        : "The CERED paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    affiliation   : "1,*"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    affiliation   : "1,*"
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
  * Shared first authorship
abstract: |
  Every day, individuals have to weigh the value of the reward when reaching a goal against the required effort.
  However, effort is not inherently aversive to all individuals, which has often been neglected by previous approaches to quantify the subjective value of effort.
  One of them is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013), which can quantify the subjective values of the difficult levels of the n-back task against the easiest level.
  We aim to replicate the analysis of Westbrook et al. (2013) with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm (CERED).
  The CERED paradigm will likely enable a more insightful investigation of interindividual differences in effort discounting, as well as the investigation of effort discounting for task types for which this is currently not possible due to their high degree of subjectivity.
